Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654

### 2016-06-28 WRITEUP/ms.tex
send to DR

In this paper, we explore the ISM properties of the quadruply imaged
quasar RXS J113151.62-123158 (hereafter RXJ1131) at
$z_\textrm{AGN}$\,$=$\,0.685, with an Einstein ring of size
1\farcs83 in radius. The foreground lensing
galaxy is an elliptical galaxy at $z_\textrm{L}$\,$=$\,0.295. The redshifts
are spectroscopically confirmed by \citet{Sluse03a}.
A black hole mass estimate of M$_{\rm BH}$\,$<$\,2\E{8}\Msun
is also reported based on X-ray observations \citep{Reis14a}.

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disk peaks \citep{Courteau97b}.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (\citetalias{Claeskens06a}; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
\citepalias{Brewer08a} and $H$-band \citepalias{Claeskens06a}, respectively.
The CO gas is thus of similar spatial
extents as in $H$ and $I$-bands.

@@

\subsubsection{Gas Mass and Gas Ratios}
% Solomon97 (ULIRGs z < 0.3): 0.4-1.5 e10 Msun
% SV05: Solomon+97: average Mgas ~7e9 Msun
% SV05: high-z: (2.5-10)e10 Msun
A total molecular gas mass of
$M_{\rm gas}^{\rm total}$ = $($1.57\pmm0.38$)$\E{10}\,\Msun is
residing within the merger system (see \Sec{caveat}).
This is comparable to those found in the
\citetalias{Combes13a} sample %(1.5\E{10}\Msun)
as well as local U/LIRGs
\citep[][\citetalias{Solomon97a}]{Sanders96a} but higher than
in local LIRGs \citepalias{Ueda14a}, as expected.
Our finding is thus consistent with previous results, where
high-$z$ galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
and is
distributed over larger spatial extents
\citepalias[\eg][]{SV05a,Riechers11a,Ivison11a}.
% gas-to-dyn ratio
% DS98: f ~ 0.16 (but w/in disc or ring of R ~ 0.5 kpc)
% Bothwell+13: f ~ 0.3? (but over larger R)
% --> ULIRGs gas fraction is even lower if average over same scale as SMGs
% Daddi10a; Tacconi10a: f_gas ? 40% in z ? 1 discs, significantly higher than local discs (but alphaCO not same as ULIRGs)
Using the dynamical mass and the total
gas mass ($M_{\rm gas}^{\rm total}$), we find a gas mass
fraction of $f_{\rm gas-dyn}$ = 0.19\pmm0.37, which is
consistent with the results reported by \citetalias{Combes13a}:
a gas fraction of 15\% in ULIRGs at 0.2\,$<$\,$z$\,$<$\,0.4 and 24\%
in those at 0.6\,$<$\,$z$\,$<$\,1.0, and those from resolved measurements of local ULIRGs \citepalias{Downes98a}.
% This implies that the gas fraction in ULIRGs at $z$$<$\,1 is
% similar to high-z starburst galaxies, but
% lower if we average over the same spatial scales (as SMGs, which
% are more extended; \citet{Bothwell13a}).
This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
similar to those in high-$z$ ``normal'' star-forming disc galaxies
\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a} as well as
high-$z$ starburst galaxies
\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}.
\defcitealias{Daddi10a}{D10}

@@

Alternatively, the relatively low SFE maybe intrinsic to RXJ1131.
In that case,  RXJ1131 may evolve into a disc galaxy with a small bulge component
in the context of theoretical simulations by \citet{Hopkins09a}, who suggest 
that the disc component in a gas-rich progenitor galaxy can survive post-merging
by lowering the \SF efficiency (and thus less efficient at removing the angular momentum of
the gas), thereby enabling a higher gas fraction to be retained and 
distributed over a larger extent.
%since there is little/no significant stellar material % (collisionless)
%available to torque away the cold gas in the disc, thus little/no angular momentum is lost, 
%and gas will rapidly reform a cold disc in the background 
%of the relaxing stellar potential.
% --> suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
% the final product will have a low bulge mass fraction.
%
%i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large).
% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\subsection{Velocity Offset and a Recoiling Black Hole}
Using the redshift deduced from the CO line 
as the systemic redshift, we find
a velocity offset of $\sim$780\,\kms with the optical lines:
the broad Mg{\scriptsize II}~2798\AA\ and the narrow 
$[$O{\scriptsize III}$]$~4959, 5007\AA\ lines \citep[$z_{\rm AGN} = 0.658$;][]{Sluse03a}.
This indicates that the broad line region (BLR) of the AGN is at a
slightly higher redshift than the host galaxy.
From the CO renzogram and channel maps in \Fig{CO21mom} and \Fig{chanmap}, the emission 
corresponding to the the line center are not co-spatial
with the optical quasar. In particular, the quasar emission forms 
the point-like images along the lensing arc, which is 
spatially offset to the NW
of the CO line center emission.
Spatial offsets between optical BLRs and CO emission are not uncommon
but such a high kinematic offset is not commonly observed.
For instance, the
velocity offset between AGNs and their hosts galaxies in 
an SDSS sample of ongoing mergers at $z$\,$<$\,0.21 is at most $\sim$410\,km/s \citep{Comerford14a}.
The same authors also suggest mechanisms
such as AGN outflows, jets, and gravitational recoil of SMBHs in post-merger
as plausible explanations for these offsets.

AGN outflows or starburst-driven winds have been observed
in \eg SMMJ1636+4057 \citep[][]{Swinbank05a}, but 
no evidence for outflows are found in RXJ1131 in the existing data. 
% an explanation due to the in/outflows arising from radiation pressure or AGN winds.
Alternatively, it can be an indication of the BH(s) orbiting the a common center in
the host galaxy.
In principle, this would only be valid if the velocity offset between the BLR and 
the narrow line of the gas in the host galaxy is consistent with its orbital velocity. 
%(\ie carrying along its accretion disc and BLR)
Since \citet{Sluse03a} only report a redshift combining the broad and narrow lines, 
% \ie it is unclear what's the velocity offset between MgII and [OIII]
the lack of a redshift from solely the BLR of the AGN precludes us from interpreting this as the favoured
explanation for the velocity offset.

@@

\subsection{Fate of RXJ1131}
The classical picture for mergers is one where they are responsible for the formation of the local 
red and passive spheroidal galaxies.
With more realistic treatments of star formation and feedbacks in recent simulations,
% ? which suppress efficient early star formation ? play a critical role in enabling disc formation in simulations.
it has been suggested that it is possible  to suppress bulge formation 
in gas-rich mergers, thereby evolving into large 
disks \citep{Springel05a, Robertson06a, Hopkins09a}.
% (bulge dominated; Springel05a, Robertson06a)
% and disc with low B/D ratio ($\sim$0.1$-$0.2; Hopkins09a).
%
%In systems that are sufficiently gas-rich, it is possible to 
%suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
%since there is little/no significant stellar material % (collisionless)
%available to torque away the cold gas in the disc, thus little/no angular momentum is lost, 
%and gas will rapidly reform a cold disc in the background 
%of the relaxing stellar potential.
%Gas, being collisional, cannot violently relax, but must
%have its angular momentum torqued away in order to dissipate and
%build a bulge by forming stars in a central starburst 
%(\ie gas loses angular momentum to stars in the
%perturbed disk and fall toward center).
% In a merger,
%this torque is primarily internal, from stars in the same disc: the
%passages and merger of the secondary induce a non-axisymmetric
%distortion in the primary stellar and gas disc. The stellar distortion
%(in a trailing resonance and close proximity to the gas response)
%efficiently removes angular momentum from the gas and allows it
%to fall to the center and form a bulge  (see also Barnes \& Hernquist
% 1996).
% A bulge will form because cold gas with no angular momentum 
% will be largely unable to form any sort of disk, and that a galaxy?s 
% worth of gas compressed to high densities and small
% radii will inevitably form a large mass in stars). 
%
Since both RXJ1131 and its companion are gas-rich
% unlikely RXJ1131 will evolve into present-day massive 
% ellipticals (M$\gtrsim$1\E{12}\,\Msun), 
% gas-poor mergers: --> present-day massive elliticals
% (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
and that the bulk of the angular momentum of the gas is  
retained in minor mergers,
it is likely that RXJ1131 will evolve into either a 
``normal'' elliptical/S0 galaxy or a large disk galaxy.  
% normal E only because gE needs ways to remove angular momentum efficiently for gas to funnel
In the latter, the stellar populations from the companion will be displaced onto the 
dominant galaxy to thicken the disk \citep[\eg][]{Lotz08a, Robertson06a}.
% disk from gas-rich major merger: \citep[\eg][]{Lotz08a, Robertson06a}.
Given that the molecular gas in 
RXJ1131 is distributed in an extended disk configuration and that its 
SFE is on the low end among other ULIRGs,  % not enough stellar material to efficiently remove ang. mom.
it is more conceivable that RXJ1131 will evolve into the
latter.
% Lotz08a: a major gas-rich merger without AGN feedback does not, by itself, produce a red and dead spheroidal galaxy
Other mechanisms e.g. formation of bar-like structures will be needed to remove the
angular momentum of the gas more efficiently to transform the gas disc into a stellar spheroid and
AGN feedbacks are also necessary to halt further activities for RXJ1131 to evolve into an 
E/S0 galaxy \citep{Lotz08a}.

>>>>

In this paper, we explore the ISM properties of the quadruply imaged
quasar RXS J113151.62-123158 (hereafter RXJ1131) at
$z_\textrm{AGN}$\,$=$\,0.685, with an Einstein ring of size
1\farcs83 in radius. The foreground lensing
galaxy is an elliptical galaxy at $z_\textrm{L}$\,$=$\,0.295. The redshifts
are spectroscopically confirmed by \citet{Sluse03a}.
A black hole mass estimate of M$_{\rm BH}$\,$<$\,2\E{8}\Msun
is also reported based on X-ray observations \citep{Reis14a}.
\defcitealias{Sluse03a}{S03}

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disk rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disk scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disk peaks \citep{Courteau97b}.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (\citetalias{Claeskens06a}; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
\citepalias{Brewer08a} and $H$-band \citepalias{Claeskens06a}, respectively.
The CO gas is thus of similar spatial
extents as in $H$ and $I$-bands.

@@

\subsubsection{Gas Mass and Gas Ratios}
% Solomon97 (ULIRGs z < 0.3): 0.4-1.5 e10 Msun
% SV05: Solomon+97: average Mgas ~7e9 Msun
% SV05: high-z: (2.5-10)e10 Msun
A total molecular gas mass of
$M_{\rm gas}^{\rm total}$ = $($1.57\pmm0.38$)$\E{10}\,\Msun is
residing within the merger system (see \Sec{caveat}).
This is comparable to those found in the
\citetalias{Combes13a} sample %(1.5\E{10}\Msun)
as well as local U/LIRGs
\citep[][\citetalias{Solomon97a}]{Sanders96a} but higher than
in local LIRGs \citepalias{Ueda14a}, as expected.
Our finding is thus consistent with previous results, where
high-$z$ galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
and is
distributed over larger spatial extents
\citepalias[\eg][]{SV05a,Riechers11a,Ivison11a}.
% gas-to-dyn ratio
% DS98: f ~ 0.16 (but w/in disc or ring of R ~ 0.5 kpc)
% Bothwell+13: f ~ 0.3? (but over larger R)
% --> ULIRGs gas fraction is even lower if average over same scale as SMGs
% Daddi10a; Tacconi10a: f_gas ? 40% in z ? 1 discs, significantly higher than local discs (but alphaCO not same as ULIRGs)
Using the dynamical mass and the total
gas mass ($M_{\rm gas}^{\rm total}$), we find a gas mass
fraction of $f_{\rm gas-dyn}$ = 0.19\pmm0.37, which is
consistent with the results reported by \citetalias{Combes13a}:
a gas fraction of 15\% in ULIRGs at 0.2\,$<$\,$z$\,$<$\,0.4 and 24\%
in those at 0.6\,$<$\,$z$\,$<$\,1.0, and those from resolved measurements of local ULIRGs \citepalias{Downes98a}.
% This implies that the gas fraction in ULIRGs at $z$$<$\,1 is
% similar to high-z starburst galaxies, but
% lower if we average over the same spatial scales (as SMGs, which
% are more extended; \citet{Bothwell13a}).
This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
similar to those in high-$z$ ``normal'' star-forming disk galaxies
\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a} as well as
high-$z$ starburst galaxies
\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}.
\defcitealias{Daddi10a}{D10}

@@

Alternatively, the relatively low SFE maybe intrinsic to RXJ1131.
In that case,  RXJ1131 may evolve into a disk galaxy with a small bulge component
in the context of theoretical simulations by \citet{Hopkins09a}, who suggest 
that the disk component in a gas-rich progenitor galaxy can survive post-merging
by lowering the \SF efficiency (and thus less efficient at removing the angular momentum of
the gas), thereby enabling a higher gas fraction to be retained and 
distributed over a larger extent.
%since there is little/no significant stellar material % (collisionless)
%available to torque away the cold gas in the disc, thus little/no angular momentum is lost, 
%and gas will rapidly reform a cold disc in the background 
%of the relaxing stellar potential.
% --> suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
% the final product will have a low bulge mass fraction.
%
%i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large).
% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\subsection{Velocity Offset and a Recoiling Black Hole}
Using the redshift deduced from the CO line 
as the systemic redshift, we find
a velocity offset of $\sim$780\,\kms with the optical lines:
the broad Mg{\scriptsize II}~2798\AA\ and the narrow 
$[$O{\scriptsize III}$]$~4959, 5007\AA\ lines \citepalias[$z_{\rm AGN} = 0.658$;][]{Sluse03a}.
This indicates that the broad line region (BLR) of the AGN is at a
slightly higher redshift than the host galaxy.
From the CO renzogram and channel maps in \Fig{CO21mom} and \Fig{chanmap}, the emission 
corresponding to the the line center are not co-spatial
with the optical quasar. In particular, the quasar emission forms 
the point-like images along the lensing arc, which is 
spatially offset to the NW
of the CO line center emission.
Spatial offsets between optical BLRs and CO emission are not uncommon
but such a high kinematic offset is not commonly observed.
For instance, the
velocity offset between AGNs and their hosts galaxies in 
an SDSS sample of ongoing mergers at $z$\,$<$\,0.21 is at most $\sim$410\,km/s \citep{Comerford14a}.
The same authors also suggest mechanisms
such as AGN outflows, jets, and gravitational recoil of SMBHs in post-merger
as plausible explanations for these offsets.

AGN outflows or starburst-driven winds have been observed
in \eg SMMJ1636+4057 \citep[][]{Swinbank05a}, but 
no evidence for outflows are found in RXJ1131 in the existing data. 
% an explanation due to the in/outflows arising from radiation pressure or AGN winds.
Alternatively, it can be an indication of the BH(s) orbiting the a common center in
the host galaxy.
In principle, this would only be valid if the velocity offset between the BLR and 
the narrow line of the gas in the host galaxy is consistent with its orbital velocity. 
%(\ie carrying along its accretion disc and BLR)
Since \citetalias{Sluse03a} only report a redshift combining the broad and narrow lines, 
% \ie it is unclear what's the velocity offset between MgII and [OIII]
the lack of a redshift from solely the BLR of the AGN precludes us from interpreting this as the favoured
explanation for the velocity offset.

@@

\subsection{Fate of RXJ1131}
The classical picture for mergers is one where they are responsible for the formation of the local 
red and passive spheroidal galaxies.
With more realistic treatments of star formation and feedbacks in recent simulations,
% ? which suppress efficient early star formation ? play a critical role in enabling disc formation in simulations.
it has been suggested that it is possible  to suppress bulge formation 
in gas-rich mergers, thereby evolving into large 
disks \citep{Springel05a, Robertson06a, Hopkins09a}.
% (bulge dominated; Springel05a, Robertson06a)
% and disc with low B/D ratio ($\sim$0.1$-$0.2; Hopkins09a).
%
%In systems that are sufficiently gas-rich, it is possible to 
%suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
%since there is little/no significant stellar material % (collisionless)
%available to torque away the cold gas in the disc, thus little/no angular momentum is lost, 
%and gas will rapidly reform a cold disc in the background 
%of the relaxing stellar potential.
%Gas, being collisional, cannot violently relax, but must
%have its angular momentum torqued away in order to dissipate and
%build a bulge by forming stars in a central starburst 
%(\ie gas loses angular momentum to stars in the
%perturbed disk and fall toward center).
% In a merger,
%this torque is primarily internal, from stars in the same disc: the
%passages and merger of the secondary induce a non-axisymmetric
%distortion in the primary stellar and gas disc. The stellar distortion
%(in a trailing resonance and close proximity to the gas response)
%efficiently removes angular momentum from the gas and allows it
%to fall to the center and form a bulge  (see also Barnes \& Hernquist
% 1996).
% A bulge will form because cold gas with no angular momentum 
% will be largely unable to form any sort of disk, and that a galaxy?s 
% worth of gas compressed to high densities and small
% radii will inevitably form a large mass in stars). 
%
Since both RXJ1131 and its companion are gas-rich
% unlikely RXJ1131 will evolve into present-day massive 
% ellipticals (M$\gtrsim$1\E{12}\,\Msun), 
% gas-poor mergers: --> present-day massive elliticals
% (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
and that the bulk of the angular momentum of the gas is  
retained in minor mergers,
it is likely that RXJ1131 will evolve into either a 
``normal'' elliptical/S0 galaxy or a large disk galaxy.  
% normal E only because gE needs ways to remove angular momentum efficiently for gas to funnel
In the latter, the stellar populations from the companion will be displaced onto the 
dominant galaxy to thicken the disk \citep[\eg][]{Lotz08a, Robertson06a}.
% disk from gas-rich major merger: \citep[\eg][]{Lotz08a, Robertson06a}.
Given that the molecular gas in 
RXJ1131 is distributed in an extended disk configuration and that its 
SFE is on the low end among other ULIRGs,  % not enough stellar material to efficiently remove ang. mom.
it is more conceivable that RXJ1131 will evolve into the
latter.
% Lotz08a: a major gas-rich merger without AGN feedback does not, by itself, produce a red and dead spheroidal galaxy
Other mechanisms e.g. formation of bar-like structures will be needed to remove the
angular momentum of the gas more efficiently to transform the gas disk into a stellar spheroid and
AGN feedbacks are also necessary to halt further activities for RXJ1131 to evolve into an 
E/S0 galaxy \citep{Lotz08a}.

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions} \label{sec:sum}
% see Hodge12_dynamics.pdf for guide

%- summarize the findings from the entire study
%    - firm conclusions
%    - speculative possibilities
We present the CO data obtained with the VLA and PdBI toward the 
quadruply-lensed optical quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65.
We investigate the cold gas kinematics and dynamics in RXJ1131
by observing its \bco and \cco line emission, which are the
two lowest rotational transitions of CO observable with current instruments.

Our results confirm the presence of a gas-rich companion, consistent with previous studies.

We find that RXJ1131 is likely a massive disturbed gas-rich disk galaxy with extreme IR
luminosity, in the process of merging 
we conclude that RXJ1131 is s a wet-wet minor merger 
between a ULIRG and an optically faint companion.

% % any further work needed to resolve the remaining problems
The intrinsically symmetric double-horned line profile, the smooth and 
symmetric velocity field/gradient seen in both the source plane from our lens model as well 
as in the image plane, and C06 model $n$=1 Sersic profile all suggest
a kinematically-order rotating disk galaxy.
Additional
characteristics such as peak velocity dispersion at the central region and a
``spider'' diagram are needed to confirm the disk morphology.

The high dispersion near the dynamical center also
suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
data are needed to confirm this.

% Gas fraction and SFH
While there is an emerging consensus on
the correlation between molecular gas content and redshift,
suggesting it as the explanation for the elevated SFR at high redshift/
the observed trend in the cosmic SFH,
we find that the gas fraction in RXJ1131 is consistent with both ULIRGs at
 0.2\,$<$\,$z$\,$<$\,0.4
and 0.6\,$<$\,$z$\,$<$\,1.0. Thus, we find no evidence of 
evolution in gas fraction.

The compactness of the emission in $V$-band (rest-frame UV)
suggests that the \SF in RXJ1131 is proceeding in a
compact region embedded within a large reservoir of molecular gas, 
which may be explained by gas inflow toward nuclear regions due to
perturbations in the disk from the companion.
Such a scenario may support the results in recent models: mergers/ULIRGs evolve into massive disks.

% consistent with the picture that BLAH, while it is also possible that BLAH.
%Our results indicate a self-consistent picture of ... followed by gravitationally instability and SF in a massive, gas-rich disk and a subsequent build-up of a central bulge through inflow triggered by disk installbilities and/or minor merger.

%Elliptical/S0 galaxies
%S0:  exhibit a bulge and disk similar to spiral galaxies, but do not show any signs of spiral arms or significant quantities of interstellar material. They consist primarily of old, population II stars and for this reason, are often misclassified as elliptical galaxies when viewed face-on.
%The origins of S0 galaxies are still unknown, but one idea is that they were originally spiral galaxies which either lost or used up their interstellar medium through interactions with another galaxy.
